### 2020-04-16 Case Studies/01_geolocation.rmd
updates to geolocation case study

```{r}
with(offlineSummary,
     smoothScatter((avgSignal - medSignal) ~ num,
                   xlab = "Number of Observations",
                   ylab = "mean - median"))
abline(h = 0, col = "#984ea3", lwd = 2)

@@

findNN <- function(newSignal, trainSubset) {
   diffs <- apply(trainSubset[ , 4:9], 1,
                  function(x) x - newSignal)
   dists <- apply(diffs, 2, function(x) sqrt(sum(x^2)) )
   closest <- order(dists)
   return(trainSubset[closest, 1:3 ])
}

@@

   for(i in 1:nrow(newSignals)) {
      trainSS <- selectTrain(newAngles[i], trainData, m = numAngles)
      closeXY[[i]] <- findNN(newSignal = as.numeric(newSignals[i, ]),
                             trainSS)
   }

   estXY <- lapply(closeXY, function(x)
                              sapply(x[, 2:3],
                                     function(x) mean(x[1:k])))
   estXY <- do.call("rbind", estXY)

@@

```{r}
surfaceSS(offlineSummary, subMacs[1], angles[1])
surfaceSS(offlineSummary, subMacs[1], angles[5])
surfaceSS(offlineSummary, subMacs[1], angles[7])

@@

```{r}
surfaceSS(offlineSummary, subMacs[3], angles[2])
surfaceSS(offlineSummary, subMacs[3], angles[5])
surfaceSS(offlineSummary, subMacs[3], angles[7])

@@

```{r}
surfaceSS(offlineSummary, subMacs[4], angles[2])
surfaceSS(offlineSummary, subMacs[4], angles[5])
surfaceSS(offlineSummary, subMacs[4], angles[7])
```

```{r}
surfaceSS(offlineSummary, subMacs[5], angles[2])
surfaceSS(offlineSummary, subMacs[5], angles[5])
surfaceSS(offlineSummary, subMacs[5], angles[7])

@@

```{r}
surfaceSS(offlineSummary, subMacs[6], angles[2])
surfaceSS(offlineSummary, subMacs[6], angles[5])
surfaceSS(offlineSummary, subMacs[6], angles[7])
```

@@

v <- 11 # n-folds
N <- 8 # num angles
K <- 20 # also choose k

@@

n_take <- 20
cv_results <- data.table(nk_err)[, 1:n_take]
colnames(cv_results) <- sapply(1:n_take, function(x) {paste0("k=", x)})
cv_results[, Angles := .I]

@@

ggplot(cv_results_flat, aes(variable, value, group = Angles)) +
   geom_line(aes(col = Angles)) +
   labs("K, N Cross-Validation Results")
```

>>>>

```{r, fig.height=8}
with(offlineSummary,
     smoothScatter((avgSignal - medSignal) ~ num,
                   xlab = "Number of Observations",
                   ylab = "mean - median"))
abline(h = 0, col = "#984ea3", lwd = 2)

@@

findNN <- function(newSignal, trainSubset) {

   diffs <- apply(trainSubset[ , 4:9], 1,
                  function(x) x - newSignal)

   dists <- apply(diffs, 2, function(x) sqrt(sum(x^2)) )

   closest <- order(dists)

   return(trainSubset[closest, 1:3 ])
}

@@

      sigValues <- suppressWarnings({ as.numeric(newSignals[i, ]) })

      closeXY[[i]] <- findNN(newSignal = sigValues,
                             trainSS)
   }

   estXY <- lapply(closeXY, function(x)
                              sapply(x[, 2:3],
                                     function(x) mean(x[1:k], na.rm = T)))
   estXY <- do.call("rbind", estXY)

@@

```{r, fig.height=4}
surfaceSS(offlineSummary, subMacs[1], angles[1])
surfaceSS(offlineSummary, subMacs[1], angles[7])

@@

```{r, fig.height=4}
surfaceSS(offlineSummary, subMacs[3], angles[2])
surfaceSS(offlineSummary, subMacs[3], angles[7])

@@

```{r, fig.height=4}
surfaceSS(offlineSummary, subMacs[4], angles[2])
surfaceSS(offlineSummary, subMacs[4], angles[7])
```

```{r, fig.height=4}
surfaceSS(offlineSummary, subMacs[5], angles[2])
surfaceSS(offlineSummary, subMacs[5], angles[7])

@@

```{r, fig.height=6}
surfaceSS(offlineSummary, subMacs[6], angles[2])
surfaceSS(offlineSummary, subMacs[6], angles[5])
surfaceSS(offlineSummary, subMacs[6], angles[7])
```

@@

v <- 11 # n-folds
N <- 6 # num angles
K <- 10 # also choose k

@@

n_take <- 10
cv_results <- data.table(nk_err)[, 1:n_take]
colnames(cv_results) <- sapply(1:n_take, function(x) {paste0("k=", x)})
cv_results[, Angles := .I]

@@

ggplot(cv_results_flat, aes(variable, value, group = Angles)) +
   geom_line(aes(col = Angles)) +
   labs("K, N Cross-Validation Results")
